Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex
BC and AB sum rules discussion

%\newcommand{\mj}{\langle m_j \rangle}
%\newcommand{\mj}{M_q^\text{jet}}
\newcommand{\mj}{M_q}
\newcommand{\mq}{m_q}
\newcommand{\mjs}{\langle m_j^2 \rangle>}

@@

The tensor charge is a fundamental property of the nucleon, at
present poorly constrained. It has been estimated in lattice
QCD (see, e.g.,
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015ow}), but
only limited information is available from direct measurements. The
way to extract the tensor charge from experimental measurements requires first
of all the extraction the so-called transversity parton distribution function,
denoted by $h_1^q(x)$~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. 
The integral of the transversity distribution
corresponds to the contribution of flavor $q$ to the tensor charge.

@@

The only other way to attain spin-flip terms in QED and QCD is taking into
account mass corrections. In fact, it is well known that transversity gives a
contribution to the structure function $g_2$ in inclusive DIS (see, e.g.,
\cite{Accardi:2009au} and references therein), and in
particular to the violation of the so-called Wandzura--Wilczek relation for
$g_2$~\cite{Wandzura:1977qf}. However, this contribution is proportional to the current quark mass
and can be expected to be very small.

@@

The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{BC,Jaffe-lectures}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1(x) \ .
\end{align}
This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. It explicitly displays the contribution from spin-flip amplitudes that is commented upon in Refs.~\cite{BC,Jaffe-lectures}, but is explicitly shown here in terms of collinear PDFs.

>>>>

\newcommand{\eg}{{\em e.g.}}
%\newcommand{\mj}{\langle m_j \rangle}
%\newcommand{\mj}{M_q^\text{jet}}
\newcommand{\mj}{M_q}
\newcommand{\mq}{m_q}
\newcommand{\mjs}{\langle m_j^2 \rangle>}

@@

The tensor charge is a fundamental property of the nucleon, at
present poorly constrained. It has been estimated in lattice
QCD (see, \eg,
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015ow}), but
only limited information is available from direct measurements. The
way to extract the tensor charge from experimental measurements requires first
of all the extraction the so-called transversity parton distribution function,
denoted by $h_1^q(x)$~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}. 
The integral of the transversity distribution
corresponds to the contribution of flavor $q$ to the tensor charge.

@@

The only other way to attain spin-flip terms in QED and QCD is taking into
account mass corrections. In fact, it is well known that transversity gives a
contribution to the structure function $g_2$ in inclusive DIS (see, \eg,
\cite{Accardi:2009au} and references therein), and in
particular to the violation of the so-called Wandzura--Wilczek relation for
$g_2$~\cite{Wandzura:1977qf}. However, this contribution is proportional to the current quark mass
and can be expected to be very small.

@@

The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{BC,Jaffe-lectures}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1(x) \ .
\end{align}
This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{BC} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe-lectures}.

Assuming the Burkhardt-Cottingham sum rule to be strictly valid, we obtain a strong constraint on the transversity function,
\begin{align}
   \int dx\, \frac{1}{x} h_1(x) = 0 \ .
\end{align}
Even if the BC sun rule is broken by a 
$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe-lectures}), we obtain that $h_1(x)/x$ must be integrable. This entails a bound on the small $x$ behavior of the transversity,
\begin{align}
  h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\end{align}
This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is as yet very limited.

{\bf [---------------- AA:  EDITED down here --------------------]}
